\section{Conclusions}

With a raise in the computational cost that has little significance,
$A^*mbush$ generates an evident upgrade in the ambush behavior.
Likewise, $P$-$A^*mbush$ shows a superior behavior over the traditional
$A^*mbush$, because it successfully increases the path diversity.


As it can be appreciated in the results, even in the worst case scenario, 
the $A^*mbush$ family never produces a result that is worse than the one made
by $A^*$. On the same line, $P$-$A^*mbush$ does not show in any
case a downgrade when compared with $A^*mbush$. 

$SAR$-$A^*mbush$ always shows the smallest incremental distance. And the
best ambush rates when the maps are large. Although, due it's computational
cost, the use of $P$-$A^*mbush$ could be more desirable when the
 processing resources are limited.

When paths are diverse, the agents performing any of the $A^*mbush$ 
methods become more naturally distributed over the map. 
Not having all the elements rounded up in a small space
can be advantageous when agents change from
one state of behavior to another. For example, if the conduct changes 
from pursue to flee, the ambush based algorithms not only allow a
better behavior, but also, they maintain the agents further away from each
other, which is a better disposition when it comes to strategies of scape.

In contrast with the pre-established conducts that are generally implemented 
for acting up in specific situations or moments of each game, the
proposed algorithms enhance the diversity of ambush situations that
can be produced as a tactical move from the agents. 

$P$-$A^*mbush$ generates an upgrade to the way the intelligence 
in the agent's behavior is perceived and $SAR$-$A^*mbush$ delivers an
even better looking one. This way, not only the paths become 
more variate, but the conduct of the agents looks better.
It makes the elements in the game act in a way that looks more
natural and perform an ambush strategy that is more effective.

For more results and experiments visit  http://www.gia.usb.ve/~kelwin/ambush/.
  