\begin{thebibliography}{4}

\bibitem{book1}
T.~Cormen, C.~Leiserson, R.~Rivest and C. Stein, \emph{Introduction to Algorithms, 3rd ed}.\hskip 1em plus 0.5em minus 0.4em\relax
  The MIT Press, 2009.
  
\bibitem{book2}
M.~Gendreau and J.~Potvin, \emph{Handbook of Metaheuristics, 2nd ed}.\hskip 1em plus 0.5em minus 0.4em\relax
  Springer, 2010.  

\bibitem{book3}
I.~Millington and J.~Funge, \emph{Artificial Intelligence for Games, 2nd ed}.\hskip 1em plus 0.5em minus 0.4em\relax
  Morgan Kaufmann Publishers, 2009.  

\bibitem{book4}
S.~Russell and P.~Norvig, \emph{Artificial Intelligence: A Modern Approach, 2nd ed}.\hskip 1em plus 0.5em minus 0.4em\relax
  	Prentice-Hall, Englewood Cliffs, NJ,, 1993.  
  
\bibitem{art1}
X.~Cui and H.~Shii, ``Direction oriented pathfinding in video games,'' \emph{International Journal of Artificial Intelligence  \& applications 2}, 2011.

\bibitem{art2}
P.~Hart, N.~Nilsson and B.~Raphael, ``Correction to “a formal basis for the heuristic determination of minimum cost paths”,'' \emph{SIGART Newsletter 37}, pp. 28--29, 1972.

\bibitem{art3}
D.~Silver, ``Cooperative pathfinding,'' \emph{ AI Game Programming Wisdom 3}, pp. 99--111, 2006.

\bibitem{art4}
R.~Teixeira, K.~Marzullo, S.~Savaje and G.~Voelker, ``In search of path diversity in isp networks,'' \emph{ IMC}, pp. 27--29, 2003.

\bibitem{art5}
W.~Ruckle, R.~Fennell, P.~Holmes and C.~Fennemore, ``Ambushing Random Walks I: Finite Models,'' \emph{Operations Research, vol 24}, No. 2, 1976.

\bibitem{art6}
W.~Ruckle, ``Ambushing Random Walks II: Continuous Models,'' \emph{Operations Research, vol 29}, No. 1, 1981.

\bibitem{art7}
I.~Woodward, ``Discretization of the Continuous Ambush Game,'' \emph{Naval Research Logistics, Vol. 50}, 2003.

\bibitem{web1}
E.~Haines, ``Point in Polygon Strategies,''
\emph{http://erich.realtimerendering.com/ ptinpoly/}, 2001.

\end{thebibliography}