\section{Related Works}
A similar problem to the one exposed in this paper is
given by \textit{Space-Time A$^*$} \cite{art3}. In this article, 
a variation of \astar is proposed. It works with an undirected
graph, induced from a grid shaped map. The cost function is common
for all agents and constant between every node pair. 

The main goal of the mentioned paper is to avoid having two 
different agents in the same node at a given instant of time.
For this variation of $A^*$, an expansion in the number of dimensions
of \astar	 is proposed: besides the positions of the agents, the elapsed
time is also taken into account. Thus, \textit{Space-Time A$^*$} has a 
considerable increment in the time and memory costs, because the size
of the search space has grown. 

Other ways of achieving ambush are explained in \cite{art5}. 
This work takes the problem of an agent that has to choose
a path across a rectangle, treated as a grid, and a second 
agent that will have to choose a sub-set of the rectangle trying
to block the path of the first one. The approach in this paper
is to create a matrix of probabilities that evaluates all the
possible combinations of paths and ambush sets, and then
choose the best strategy for both agents through the minimax
algorithm.

\cite{art6} and \cite{art7} approach the previous problem with
sets of continuous nature. In the first work, discrete versions of 
the game model are proposed. Afterwards they are
used to find optimal solutions that satisfy the original
continuous model. The work in \cite{art7} proposes various sets
of solutions for conditions that were not considered in \cite{art6}.

Previous works show exponential search spaces, deriving
in high computational costs. The $A^*mbush$ family is proposed
as an effective method with lower computational order, that can
be used in more general conditions.